A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex
transfer to desktop

For an integer $n\in\ZZ$ consider the homomorphism $\alpha_n\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ under which $w_1$ has weight $1$ and $w_2$ has weight $-1$ and the projection on the second factor is given by $z\mapsto z^n$.

@@

\begin{thm}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{thm}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}

>>>>

Recall, the $R$-symmetry group is $G_R = \SU(2) \times \U(1)$.
For any integer $n\in\ZZ$ consider the homomorphism 
\[
\begin{array}{cccccc}
\alpha_n & \colon & \U(1) & \rightarrow & \SU(2)\times \U(1)\\
& & z & \mapsto & \left({\rm diag}(z^{2n}, z^{-2n}) , z^{-2n+1} \right)
\end{array}
\]
under which $w_1$ has weight $1$ and $w_2$ has weight $-4n+1$.

@@

\begin{thm}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{thm}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}
